### 2020-08-15 design.tex
10.5pages

\subsection{Design Principal}
To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}

\begin{itemize}
    \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers. All input images are processed simultaneously and separately, with the information from other images for reference, throughout the network. Another important feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are performed individually for each image (or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power. This trait also enables the same network to adapt any number of input images. On one hand, this gives our model the ability to adapt to the uncertainty of the number of available images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, our model can learn correlations between certain features and strokes from the training data, decomposing the SR problem and making it a lot less challenging. We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalances of data. The loss functions in training is also redesigned. The mean square error (MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels. Our solution is putting a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
  \end{itemize}

>>>>

\subsection{Design Principle}
To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}

\begin{itemize}
    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network. The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
    \item \textbf{Inconsistency problem, model Complexity and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters. This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames. Furthermore, this allows variations in the number of input images.
    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, instead of using Mean Square Error(MSE) as the loss function, we put a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
  \end{itemize}

### 2020-08-15 evaluation.tex
10.5pages

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.

@@

In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition (OCR) services to evaluate the accuracy. The model with traditional lens without optical zoom (hereafter referred as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom (hereafter referred as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens in both day and night time. The PSNR is higher than 10 as well. OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs. For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical lens. The performance is relatively consistent in both day and night time. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.

In the optical zoom group, the accuracy of the model dropped drastically at 7m distance. Increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.). It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.

\subsection{Performance In Random Environments}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments. The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}. For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens. From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical lens. This verifies the efficiency of our model for environment adaption.

We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances. As the model is trained initially on the 5m group data, it performs especially well at this distance, while the accuracy at other distances experience certain levels of decrease. Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.
\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in the random environment using traditional lens and optical Lens.}
    \label{fig:control}
\end{figure}

>>>>

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two Custom Off-The-Shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.

@@

In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio(PSNR) to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy. The model with traditional lens without optical zoom (hereafter referred as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom (hereafter referred as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens and at 6m with optical lens. Performances are relatively consistent in both day and night time, while increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.). It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.

\subsection{Performance In Random Environments}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments. The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}. We can observe that the model performs best in daytime and at closer distances. For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens. From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical lens. This verifies the efficiency of our model for environment adaption.

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in the random environment using traditional lens and optical Lens.}
    \label{fig:control}
\end{figure}

### 2020-08-15 implementation.tex
change reallife fig
cl
10.5pages

\subsection{Data Collection}
\label{sec-experiment-setting}

In our experiment, we are forced to collect the training dataset on our own instead of using public datasets. Because of our unique application, to the best of our knowledge there is no publicly available image dataset built for shoulder-surfing. Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them. Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model. When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours). There is no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data. %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.

Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Figure~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
         \label{fig-train-single-4}
         }
    % \subfigure[ground truth]{
     %    \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
      %   \label{fig-train-single-5}
       %  }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}

\subsection{Experiment Setting}
As a result of these observations, we have to collect images in varied environments. Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lenses (for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming. Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation. An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos. Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters.

As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation. An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (Distance between phones is shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.). We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter. The position of the phones is also a crucial factor in this parameter, and we avoid extreme settings, e.g. having the sunlight directly shining on the screen. We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels). This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

\subsection{Model Specifications}
It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (less pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features. Thus, the specifications of our model are only for reference and may not work when reproduced on another phone.

@@

\subsection{Training Process}
Because of the difficulties in discovering the patterns among the blurry images, the training process is not so straightforward and somewhat time-consuming. Our approach is as follows: we first collect 60,000 images at a stationary experiment setting and train the model with it, as mentioned in Sec~\ref{sec-experiment-setting}, until we get satisfactory results on the test dataset. The model should be able to handle this task easily. After that, we use transfer learning methods to fine tune the model in order to fit different environmental parameters. We add a small percentage of image data from another similar experiment setting into the training data and resume training. When the model stabilizes, continue adding data from the same setting until the model can equally process data from the two image collections. Note that in this process the model will tend to extract false features, displaying wrong but clear texts as result. This phenomenon can be mitigated with dropout and normalization layers. As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 1.8m and 1.2m range in the training process, the model fits 1.5m photos easily. After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.

>>>>

In our experiment, we are forced to collect the training dataset on our own instead of using public datasets, as there is no publicly available image dataset built for shoulder-surfing to the best of our knowledge, and because of the uniqueness of our application, i.e. blurriness, targeting characters, working with burst mode snapshots, etc., we cannot find any publicly avaliable substitudes.
%Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

%Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model.
 %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.

\subsection{Experiment Setting}
\label{sec-experiment-setting}
Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lenses (for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming. Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation. An app runs inside the attacker's phone, taking photos in burst mode repeatedly (20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. Screenshots were taken in the victim's phone as ground truth for training and evaluation. An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
\begin{figure}
	\centering
	\includegraphics[width=0.46\textwidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

The data was collected at different times of the day and night, with different illumination and at different positions and angles(tilting no more than 30 degrees). We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels), modifying these environmental parameters every 2,000 images. This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

\subsection{Model Specifications}
It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (less pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features. Thus, the specifications of our model are only for reference and may not work when reproduced on another phone. Also, we may need to repeat the data collection and training phases when switching to another phone model.

@@
